Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
minor: implemented one Henning's todo
temp

\newcommand{\skug}[1]{{\color{blue}[SK: #1]}}
\newcommand{\hmey}[1]{{\color{red}[HM: #1]}}
\newcommand{\AB}[1]{{\color{purple}[AB: #1]}}
\newcommand{\willchange}[1]{{\color{orange}[AB: #1]}}

@@

\author{\IEEEauthorblockN{Svetlana Kulagina}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-2108-9425}
\and
\IEEEauthorblockN{Anne Benoit}
\IEEEauthorblockA{\textit{ENS Lyon, France} \\
ORCID: 0000-0003-2910-3540
}
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID
\and
\IEEEauthorblockN{Henning Meyerhenke}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-7769-726X}
}

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
\new{Workflow tasks themselves have no memory requirements for their computations,
but they have input and output files that need to be stored in the memory.}
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{requires deleting all input files when the task starts and adding all output files to memory.}

@@

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, \new{is our own previous work~\cite{DBLP:conf/icpp/KulaginaMB24}.}
\new{Yet, in that paper we only propose} a partitioning-based mapping of the workflow, without processor reuse.
\new{Since a processor is idle after a workflow partition has finished its execution,
there is no need in Ref.~\cite{DBLP:conf/icpp/KulaginaMB24} for communication buffers to store data
that should be \new{exchanged} between processors when tasks are ready to execute.}

@@

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The procedure involves building a first (static) schedule with HEFT, periodic resource monitoring, 
    and rescheduling the remaining tasks. 
%    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
%    For each resource group, there is an own scheduler, and an overall global scheduler responsible for distributing
%    tasks to groups.
%    The static heuristic is HEFT with earliest start time as priority.
    Upon rescheduling, a new mapping is calculated from scratch, and this mapping is accepted if the resulting makespan
    is smaller than the previous one.
    \todo[inline]{Maybe mention: from scratch computation because of tiny workflows??}
%    The experiments were conducted on a single workflow with 10 tasks.
%
    % The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    %The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

>>>>

\newcommand{\skug}[1]{{\color{blue}[SK: #1]}}
\newcommand{\hmey}[1]{{\color{red}[HM: #1]}}
\newcommand{\AB}[1]{\todo[inline]{{\color{purple}[AB: #1]}}}

@@

\author{\IEEEauthorblockN{Svetlana Kulagina}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-2108-9425}
\and
\IEEEauthorblockN{Anne Benoit}
\IEEEauthorblockA{\textit{ENS Lyon \& IUF, France} \\
ORCID: 0000-0003-2910-3540
}
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID
\and
\IEEEauthorblockN{Henning Meyerhenke}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-7769-726X}
}

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
\new{Workflow tasks themselves have no memory requirements for their computations,
but they have input and output files that need to be stored in the memory.}
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{requires deleting all input files when the task starts and adding all output files to memory.}
\AB{Is it not when task completes? We need input files while processing the task, correct?}

@@

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, \new{is our own previous work~\cite{DBLP:conf/icpp/KulaginaMB24}.}
\new{Yet, in that paper we only propose} a partitioning-based mapping of the workflow, without processor reuse.
\new{Since a processor is idle after a workflow partition has finished its execution 
in~\cite{DBLP:conf/icpp/KulaginaMB24},
there is no need for communication buffers to store data
that should be \new{exchanged} between processors when tasks are ready to execute.}

@@

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The procedure involves building a first (static) schedule with HEFT, periodic resource monitoring, 
    and rescheduling the remaining tasks. 
%    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
%    For each resource group, there is an own scheduler, and an overall global scheduler responsible for distributing
%    tasks to groups.
%    The static heuristic is HEFT with earliest start time as priority.
    Upon rescheduling, a new mapping is computed from scratch, 
    and this mapping is accepted if the resulting makespan
    is smaller than the previous one.
    \new{Only small workflows with less than 100 tasks are considered, hence it is possible to do
    these repeated computations from scratch in a reasonable time. }
%    The repeated recomputation from scratch is feasible, because the largest workflow size tested is 100 task big.}
%    \todo[inline]{Maybe mention: from scratch computation because of tiny workflows??}
%%    The experiments were conducted on a single workflow with 10 tasks.
%
    % The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    %The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.
